---
title: "R package"
author: "Ifesinachi Nwatu"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
devtools::install("C:/Users/Princ/Downloads/MATH4753/Package/mypackage")  # Replace "path/to/mypackage" with the actual path to your package



```

```{r}
library(mypackage)

```

```{r r setup, include=FALSE}

library(mypackage)

```



# Introduction



I will assume your package is called **MYPAC** and you have packaged and documented functions `myf1`, `myf2`, `myf3` and `myf4`.

Your actual package name and functions will obviously be called something else.

# First function

Please place your first function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r}
mypackage::t_test_example(x = c(1, 2, 3), y = c(4, 5, 6))


```


# Second function

Please place your second function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r second, }
mypackage::mean_sd(x = c(1, 2, 3, 4, 5))


```


# Third function

Please place your third function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r third, }
mypackage::reverse_string(str = "Hello, world!")


```


# Fourth function

Please place your fourth function in the r chunk in the following way:

Once you are ready please remove the option `eval = FALSE`

```{r fourth,}
# Create a data frame for demonstration
demo_data <- data.frame(x = 1:10, y = 2 * (1:10) + rnorm(10))

# Use the function
mypackage::lm_summary(formula = y ~ x, data = demo_data)


```

# The github repository



This is the address of my GITHUB repository:
<https://github.com/Ifesinachi12/Math4753-Package.git>

Replace this with your own address.


